\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-09-21 manuscript.Rmd

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower")
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```

>>>>

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal, tl.cex = 8,tl.srt = 90 )
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```
